---
title       : Top Ten Occupations
subtitle    : Find the best and worst occupations based on education level
author      : Annette Crist
job         : Coursera Developing Data Products Course
framework   : dzslides        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight      # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []     # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---


## Top Ten Occupations

```{r, echo=FALSE}

## Initialization
library(reshape2)
library(ggplot2)
library(RColorBrewer)
emp_names <- c("Soc.Code","X2012","X2022","Delta","Delta.Percent",
               "GrowthReplaceOpennings","MedianWage.X2012","Education")
emp_data <- read.csv("~/EmpDataPres/Slides/Presentation/Employment Projections.csv", stringsAsFactors=FALSE,
                     na.strings = "N/A")[,2:9]
names(emp_data) <- emp_names
emp_data <- emp_data[,c("Education","MedianWage.X2012")]

emp_data <- emp_data[!is.na(emp_data$MedianWage.X2012),]
emp_data$MedianWage.X2012 <- gsub(">=","",emp_data$MedianWage.X2012)
emp_data$MedianWage.X2012 <- as.numeric(gsub(",","",emp_data$MedianWage.X2012))
emp_data <- emp_data[order(emp_data$MedianWage.X2012,decreasing = TRUE, na.last = FALSE),]
emp_data$Education <- as.factor(emp_data$Education)
eval <- melt(emp_data, id ="Education", measure.vars = "MedianWage.X2012")
eval <- dcast(eval, Education ~ variable, mean)
eval <- eval[order(eval$MedianWage.X2012),]

```

---


### Is Education Overrated?

* Does school seem like a drag?
* Ever wonder what job you could get if you quit now?
* What if you like school but don't know what career path to choose.
* How much schooling do I need to make top dollar?



--- .class #id 


### Don't Drop Out.

```{r, echo=FALSE}
## Lowest to Highest Earning Comparison
x <- round((eval[eval$Education=="Doctoral or professional degree","MedianWage.X2012"] -
        eval[eval$Education=="Less than high school","MedianWage.X2012"])/
    eval[eval$Education=="Doctoral or professional degree","MedianWage.X2012"],2)
##  Lowest to Bachelor's Degree
x2 <- round((eval[eval$Education=="Bachelor's degree","MedianWage.X2012"] -
           eval[eval$Education=="Less than high school","MedianWage.X2012"])/
    eval[eval$Education=="Bachelor's degree","MedianWage.X2012"],2)
##  High School diploma to Highest Earning Comparison

```

*  According to the 2012 Labor and Statistics Data there is a `r paste(x * 100)`% difference in wages between high school drop-outs and those with doctoral or professional degrees. 
* Even getting a bachelor's degree improves your earnings by `r paste(x2 *100)`%.  

--- .class #id 


### Education Does Pay Off!

```{r Figure 1,echo=FALSE,cache.lazy=TRUE, warning=FALSE, message=FALSE,fig.height=5,fig.width=9}

g <- ggplot(eval,aes(x = reorder(Education, MedianWage.X2012), y = MedianWage.X2012, fill = factor(Education))) +
    geom_bar(stat = "identity") + 
    scale_fill_brewer(palette = "Set3") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
    labs(x= "",y = "Mean Wage (Dollars)") +
    guides(fill = FALSE) +
    labs(title= "Average Wages by Education Level")

print(g)


```





--- .class #id 


### Check Out the Top Ten Occupations Website for More Information.

### [Top Ten] (https://alc11.shinyapps.io/EmpDataApp)




